HGP analysis: fit model

### 2019-03-15 rick/final/3_fit_model_compareModels.Rmd
update

}
#modified from gcat
fit_glm <- function(..., LF, trait){
  snp <- c(...)
  ind <- !is.na(snp) #logical index vector
  snp_no_na <- snp[ind]
  LF_no_na <- LF[ind,]
  p0 <- rep(NA, length(snp))
  p1 <- rep(NA, length(snp))
  trait_no_na <- trait[ind]
  b0 <- lreg(snp_no_na, LF_no_na) #coefficients from logreg 
  b1 <- lreg(snp_no_na, cbind(LF_no_na, trait_no_na))
  est0 <- .Call("mv", LF_no_na, b0)
  est1 <- .Call("mv", cbind(LF_no_na, trait_no_na), b1)
  p0[ind] <- exp(est0)/(1+exp(est0))
  p1[ind] <- exp(est1)/(1+exp(est1))

@@

@@

```{r,fig.height = 10, fig.width = 6}
#plot diff
plt <- merge(data_fit, data_fit_Pop_dich, by=c('rsID'), suffixes = c('LFA_Full','Pop_Dich'))

>>>>

}
#modified from gcat
fit_glm <- function(..., LF, trait){
  snp <- c(...)
  ind <- !is.na(snp) #logical index vector
  snp_no_na <- snp[ind]
  LF_no_na <- LF[ind,]
  p0 <- rep(NA, length(snp))
  p1 <- rep(NA, length(snp))
  trait_no_na <- trait[ind]

  b0 <- lreg(snp_no_na, LF_no_na) #coefficients from logreg 
  b1 <- lreg(snp_no_na, cbind(LF_no_na, trait_no_na))
  est0 <- .Call("mv", LF_no_na, b0)
  est1 <- .Call("mv", cbind(LF_no_na, trait_no_na), b1)
  p0[ind] <- exp(est0)/(1+exp(est0))
  p1[ind] <- exp(est1)/(1+exp(est1))

@@

beta1<-ggplot(plt, aes(b, bPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='Pop', y='PCA')+ggtitle('Beta')
beta2<-ggplot(plt, aes(bLFA, bPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='PCA')+ggtitle('Beta')
beta3<-ggplot(plt, aes(bLFA, b))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Beta')
betas <- plot_grid(beta1,beta2,beta3,nrow=1)

af1<-ggplot(plt, aes(1-num_zeros/2504, bLFA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='AF', y='LFA')+ggtitle('Beta')+xlim(c(0,0.3))
af2<-ggplot(plt, aes(1-num_zeros/2504, bPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='AF', y='PCA')+ggtitle('Beta')+xlim(c(0,0.3))
af3<-ggplot(plt, aes(1-num_zeros/2504, b))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='AF', y='Pop')+ggtitle('Beta')+xlim(c(0,0.3))
af <- plot_grid(af1,af2,af3,nrow=1)
af
ggsave('./Beta_AF.jpg', height=4, width=8)

plt <- plt[which(plt$num_zeros < 2501),]

beta1<-ggplot(plt, aes(b, bPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='Pop', y='PCA')+ggtitle('Beta')
beta2<-ggplot(plt, aes(bLFA, bPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='PCA')+ggtitle('Beta')
beta3<-ggplot(plt, aes(bLFA, b))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Beta')
betas2 <- plot_grid(beta1,beta2,beta3,nrow=1)

af1<-ggplot(plt, aes(1-num_zeros/2504, bLFA))+geom_point(shape=1)+labs(x='AF', y='LFA')+ggtitle('Beta')+xlim(c(0,0.3))
af2<-ggplot(plt, aes(1-num_zeros/2504, bPCA))+geom_point(shape=1)+labs(x='AF', y='PCA')+ggtitle('Beta')+xlim(c(0,0.3))
af3<-ggplot(plt, aes(1-num_zeros/2504, b))+geom_point(shape=1)+labs(x='AF', y='Pop')+ggtitle('Beta')+xlim(c(0,0.3))
af2 <- plot_grid(af1,af2,af3,nrow=1)
af2
ggsave('./Beta_AF2.jpg', height=4, width=8)

makePlot <- function(x,y,xlab,ylab,title) {
p <- ggplot(plt, aes(x, y)) + 
  geom_abline(color='grey') +
  geom_point(shape=1) +
  labs(x=xlab, y=ylab) +
  ggtitle(title)

return(p)
}

p1 <- makePlot(plt$dev0LFA, 
               plt$dev0PCA, 
               'Null Deviance LFA', 
               'Null Deviance PCA', 
               'Null Model')
p2 <- makePlot(plt$devdiffLFA, 
               plt$devdiffPCA, 
               'Deviance LFA', 
               'Deviance PCA', 
               'Deviance')

p2.2<-ggplot(plt, aes(devdiffLFA, devdiffPCA))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='PCA')+ggtitle('Deviance Zoom')+xlim(c(0,30))+ylim(c(0,30))

p3<-ggplot(plt, aes(bLFA, bPCA, color=1-num_zeros/2504))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='PCA')+ggtitle('Beta')
pp1 <- plot_grid(p1,p2,p2.2,p3,ncol=1)

p1<-ggplot(plt, aes(dev0LFA, dev0))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Null Model')
p2<-ggplot(plt, aes(devdiffLFA, devdiff))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Deviance')
p2.2<-ggplot(plt, aes(devdiffLFA, devdiff))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Deviance Zoom')+xlim(c(0,30))+ylim(c(0,30))
p3<-ggplot(plt, aes(bLFA, b, color=1-num_zeros/2504))+geom_abline(color='grey')+geom_point(shape=1)+labs(x='LFA', y='Pop')+ggtitle('Beta')
pp2 <- plot_grid(p1,p2,p2.2,p3,ncol=1)

@@

```{r,fig.height = 10, fig.width = 6}
#plot diff
plt <- merge(data_fit[-2], data_fit_Pop_dich[-2], by=c('rsID'), suffixes = c('LFA_Full','Pop_Dich'))
